\bf Aggregated Financial Forecasting Calculation in Human-Computer Distributed Computing

### 2020-04-07 Aggregated-Financial-Forecasting-Calculation-in-Human-Computer-Distributed-Computing/paper.tex
Conclusions were added.

Users have the opportunity to vote for future changes in the particular financial time series. The vote is collected on a remote server. Voters are classified in four common groups: High voting frequency and high guess rate users (group $a$); Low voting frequency and high guess rate users (group $b$); High voting frequency and low guess rate users (group $c$); Low voting frequency and low guess rate users (group $d$). This classification is the base of the aggregated forecasting proposed in this research. Each group of the voters participates with a different coefficient in the final forecast calculation. 
%
\begin{equation}
\begin{array}{l}
f(x) = \frac{w_{a}}{n_{a}} \sum_{a=1}^{n_{a}} x_{a} + \frac{w_{b}}{n_{b}} \sum_{b=1}^{n_{b}} x_{b} + \frac{w_{c}}{n_{c}} \sum_{c=1}^{n_{c}} x_{c} + \frac{w_{d}}{n_{d}} \sum_{d=1}^{n_{d}} x_{d} \\
\text{where} \\
N = n_{a} + n_{b} + n_{c} + n_{d} \\
w_{a} + w_{b} + w_{c} + w_{d} = 1
\end{array}
\label{equ01}
\end{equation}
%
When a particular forecast should be issued single votes for the particular situation are taken and they are aggregate by groups to form the forecast. The forecast is in the form of chance the price to go up (value between 0.0 and 1.0, Eq. \ref{equ01}) and the opposite chance for the price to go down (also between 0.0 and 1.0). The sum of the two chances gives 1. The vector $x$ in Eq. \ref{equ01} is a binary vector. It has 1 for each vote of a user who thinks that the price will go up and it has 0 for each vote of the user who thinks that the price will go down. The total number of available votes for a particular forecasted event is $N$. The size of each group is given by the small letter $n$ with an index. Each group participate in the aggregated forecast with a given coefficient presented by the small letter $w$ with and index. The values of the coefficients are subject to a multicriteria problem and are chosen by the decision-makers.
%
\section{Experiments \& Results}
%
\section{Conclusions}
%
% ---- Bibliography ----
%
% BibTeX users should specify bibliography style 'splncs04'.
% References will then be sorted and formatted in the correct style.
%
% \bibliographystyle{splncs04}
% \bibliography{mybibliography}
%
\begin{thebibliography}{8}

>>>>

Users have the opportunity to vote for future changes in the particular financial time series. The vote is collected on a remote server. Voters are classified in four common groups: High voting frequency and high guess rate users (group $a$); Low voting frequency and high guess rate users (group $b$); High voting frequency and low guess rate users (group $c$); Low voting frequency and low guess rate users (group $d$). This classification is the base of the aggregated forecasting proposed in this research. Each group of the voters participates with a different coefficient in the final forecast calculation. 
%
\begin{equation}
\begin{array}{l}
f(x) = \frac{w_{a}}{n_{a}} \sum_{a=1}^{n_{a}} x_{a} + \frac{w_{b}}{n_{b}} \sum_{b=1}^{n_{b}} x_{b} + \frac{w_{c}}{n_{c}} \sum_{c=1}^{n_{c}} x_{c} + \frac{w_{d}}{n_{d}} \sum_{d=1}^{n_{d}} x_{d} \\
\text{where} \\
N = n_{a} + n_{b} + n_{c} + n_{d} \\
w_{a} + w_{b} + w_{c} + w_{d} = 1
\end{array}
\label{equ01}
\end{equation}
%
When a particular forecast should be issued single votes for the particular situation are taken and they are aggregate by groups to form the forecast. The forecast is in the form of chance the price to go up (value between 0.0 and 1.0, Eq. \ref{equ01}) and the opposite chance for the price to go down (also between 0.0 and 1.0). The sum of the two chances gives 1. The vector $x$ in Eq. \ref{equ01} is a binary vector. It has 1 for each vote of a user who thinks that the price will go up and it has 0 for each vote of the user who thinks that the price will go down. The total number of available votes for a particular forecasted event is $N$. The size of each group is given by the small letter $n$ with an index. Each group participate in the aggregated forecast with a given coefficient presented by the small letter $w$ with and index. The values of the coefficients are subject to a multicriteria problem and are chosen by the decision-makers.
%
\section{Experiments \& Results}
%
\section{Conclusions}
%
The proposed aggregated financial forecasting based on human-computer mobile distributed computing shows to be very promising in situations where pure technical analysis has weaknesses. The main disadvantage is related to the lack of a strict scientific explanation of how human intuition works. Even with such a disadvantage, the proposed forecasting approach may be applied successfully in many practical situations.

As further directions of research, it will be interesting nonlinearities to be investigated in the way in which values of the four groups are calculated to a single prediction. Another interesting direction of further research is related to the estimation of multi-criteria coefficients according decision-makers preferences.
%
% ---- Bibliography ----
%
% BibTeX users should specify bibliography style 'splncs04'.
% References will then be sorted and formatted in the correct style.
%
% \bibliographystyle{splncs04}
% \bibliography{mybibliography}
%
\begin{thebibliography}{8}
